### 2017-01-10 README.Rmd
added worms data source via worrms pkg, bumped patch version added mehods for worms to children, classification, comm2sci, sci2comm, synonyms

>>>>

	<td style="text-align:left;">World Register of Marine Species (WoRMS)</td>
	<td style="text-align:left;"><code>worms</code></td>
	<td style="text-align:left;"><a href="http://www.marinespecies.org/aphia.php?p=webservice">link</a></td>
	<td style="text-align:left;">NatureServe</td>
	<td style="text-align:left;"><code>natserv</code></td>
	<td style="text-align:left;"><a href="https://services.natureserve.org/BrowseServices/getSpeciesData/getSpeciesListREST.jsp">link</a></td>
